### 2020-07-12 thesis/thesis.tex
[thesis] Algebraic Theories

%%%%% WLASNE DODATKOWE PAKIETY
% \usepackage{graphicx,listings,tikz}
\usepackage{syntax}
\usepackage{mathalfa}
\usepackage{textcomp}

\usepackage[backend=bibtex]{biblatex}
\addbibresource{mybib.bib}
%
%%%%% WŁASNE DEFINICJE I POLECENIA
%
\theoremstyle{definition} \newtheorem{definition}{Definition}[chapter]
\theoremstyle{remark} \newtheorem{remark}[definition]{Observation}
\theoremstyle{plain} \newtheorem{theorem}[definition]{Theorem}
\theoremstyle{plain} \newtheorem{lemma}[definition]{Lemma}
%\renewcommand \qedsymbol {\ensuremath{\square}}
% ...
%%%%%

@@

    Sigma-Signatures, Sigma-Terms, Sigma-Equations, Interpretations, Models, Free models

>>>>

%%%%% WLASNE DODATKOWE PAKIETY
% \usepackage{graphicx,listings,tikz}
\usepackage{syntax}
\usepackage{mathalfa}
\usepackage{textcomp}
\usepackage{stmaryrd}

\usepackage[backend=bibtex]{biblatex}
\addbibresource{mybib.bib}
%
%%%%% WŁASNE DEFINICJE I POLECENIA
%
\theoremstyle{definition} \newtheorem{definition}{Definition}[chapter]
\theoremstyle{remark} \newtheorem{remark}[definition]{Observation}
\theoremstyle{plain} \newtheorem{theorem}[definition]{Theorem}
\theoremstyle{plain} \newtheorem{lemma}[definition]{Lemma}
%\renewcommand \qedsymbol {\ensuremath{\square}}

\newcommand{\mathVar}[1]{{\operatorname{\mathit{#1}}}}

% ...
%%%%%

@@

    \begin{definition}{\mathVar{Signature}}

    A \textit{signature $ \Sigma $} is given by a collection of operation symbols $ op_{i} $
    with associated parameters $ P_{i} $ and arities $ A_{i} $, where
    $ P_{i} $ and $ A_{i} $ are objects in the category of our interest.
    We will write an operation as $ op_{i} : P_{i} \rightsquigarrow A_{i} $

    \end{definition}

    \begin{definition}{$\mathVar{\Sigma-terms}$}

    Collection of $\mathVar{\Sigma-terms}$ is a free algebra with a generator $X$
    for a functor $ \mu H_{\Sigma} $ that maps objects into trees over a given
    signature $ \Sigma $ and morphisms into folds over trees.

    \end{definition}

    \begin{definition}{$ \mathVar{\Sigma-Equation} $}

        A $ \mathVar{\Sigma-Equation} $ is an object X and a pair of
        $\mathVar{\Sigma-terms}$ $l, r \in Tree_{\Sigma}(X)$, written as

        $ X $ $|$ $l = r$

    \end{definition}

    \begin{definition}{Algebraic Theory}

    An \textit{algebraic theory} $T = (\Sigma_{T}, \mathcal{E}_{T})$, is given by
    a signature $\Sigma_{T}$ and a collection $\mathcal{E}_{T}$ of
    $\mathVar{\Sigma_{T}-equations}$. For clarity we will usually omit T subscript

    \end{definition}

    \begin{definition}{Interpretation}

    An \textit{interpretation $I$ over a given signature $\Sigma$} is given by
    a carrier object $|I|$ and for each $ op_{i} : P_{i} \rightsquigarrow A_{i} $
    in $\Sigma$ a map

    $ {\llbracket op_{i} \rrbracket}_I : P_{i} \times{} {|I|}^{A_{i}} \rightarrow |I| $

    Interpretation may be naturally extended to $\mathVar{\Sigma-terms}$, such
    that a given $\mathVar{\Sigma-term}$ $X$ $|$ $t$ is interpreted by a map

    $ {\llbracket X | t \rrbracket}_I : {|I|}^{k} \rightarrow |I| $

    TODO actually define the map as a projection on variables and
    map composition on compound terms.

    where ${|I|}^{k}$ is an k-ary product in our category, assuming that all of the
    necessary products exist.

    \end{definition}

    TODO Models, Free models
